---
title: '5243'
output: html_document
---
What made people happy? Here are the top frequent words that made people happy in their life. Moreover, we want to know for people in different life stages, what moments in life will make them happy.
```{r,warning= FALSE, message = FALSE, echo=FALSE}
library(tidyverse)
library(tidytext)
library(DT)
library(scales)
library(wordcloud2)
library(gridExtra)
library(ngram)
library(shiny) 
```



```{r load data, warning=FALSE, message=FALSE,echo=FALSE}
hm_data <- read_csv("../output/processed_moments.csv")

urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
demo_data <- read_csv(urlfile)
```

```{r combining data, warning=FALSE, message=FALSE,echo=FALSE}
hm_data <- hm_data %>%
  inner_join(demo_data, by = "wid") %>%
  select(wid,
         original_hm,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         ground_truth_category, 
         predicted_category,
         text) %>%
  mutate(count = sapply(hm_data$text, wordcount)) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(marital %in% c("single", "married")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_3 = "3m", hours_24 = "24h"))
```


```{r bag of words, warning=FALSE, message=FALSE,echo=FALSE}
bag_of_words <-  hm_data %>%
  unnest_tokens(word, text)

word_count <- bag_of_words %>%
  count(word, sort = TRUE) 

word_count <- word_count[which(word_count$word!='feel'),]
word_count <- word_count[which(word_count$word!='enjoyed'),]
word_count <- word_count[which(word_count$word!='time'),]
word_count <- word_count[which(word_count$word!='day'),]
word_count <- word_count[which(word_count$word!='moment'),]
word_count <- word_count[which(word_count$word!='found'),]
word_count <- word_count[which(word_count$word!='favorite'),]
word_count <- word_count[which(word_count$word!='finally'),]

word_counts <- bag_of_words %>%
  count(predicted_category,word, sort = TRUE) %>%
  ungroup()

word_counts <- word_counts[which(word_counts$word!='feel'),]
word_counts <- word_counts[which(word_counts$word!='enjoyed'),]
word_counts <- word_counts[which(word_counts$word!='time'),]
word_counts <- word_counts[which(word_counts$word!='day'),]
word_counts <- word_counts[which(word_counts$word!='moment'),]
word_counts <- word_counts[which(word_counts$word!='found'),]
word_counts <- word_counts[which(word_counts$word!='favorite'),]
word_counts <- word_counts[which(word_counts$word!='finally'),]
```


There are some words in the survey that can not tell us what really makes people happy. For example, all the words to describe happiness which includes "fun", "enjoyed","favorite", etc. Also, some verbs like "feel" and "found", etc. I exclude those words from the word_count list. 

##Topic Modeling 
```{r,echo=FALSE,message=FALSE,warning=FALSE}
#word_counts <- word_counts[-2,]
chapters_dtm <- word_counts %>%
  cast_dtm(predicted_category, word, n)

#chapters_dtm
```

```{r,echo=FALSE}
library(topicmodels)
chapters_lda <- LDA(chapters_dtm, k = 3, control = list(seed = 1234))
#chapters_lda
```

```{r,echo=FALSE}
chapter_topics <- tidy(chapters_lda, matrix = "beta")
#chapter_topics
```


```{r,echo=FALSE}
top_terms <- chapter_topics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

#top_terms
```


```{r,echo=FALSE}
library(ggplot2)

top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

I divided those texts into three topics and the above graph showed top 10 most relevant words for each topic. The topic 1 is essentially about Entertainment. People are happy because of doing some activities like playing game, eating delicious food or watching a movie. The topic 2 is about Family, people are happy because of their family members like their wife, husband, childrens and dogs. The topic 3 is about Properties and Achievements. People are happy because they did something they feel proud of like landing a job, bought a car etc. 


##Overview of the frequent words


```{r,echo=FALSE}
word_count %>%
      slice(1:200) %>%
      wordcloud2(size = 0.6,
                 rotateRatio = 0,backgroundColor = "grey")
```
The top frequent words are relating to "friend", "family", "home", "birthday", "job", "dinner", "husband", "daughter",etc. These words showed the core source of happiniess for these people and it reflects what they value the most in their lives. Most of their happiness are relating to friends, Thus, friends play an indispensible role throughout people's lives no matther what ages they are in, no matter what gender they are, and no matter if they are single or married.   \newline


We can also have a numberical visulization of the Top frequent words and their frequncies by looking at the bar chart below. 
```{r,echo=FALSE}
word_count %>%
      slice(1:20) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      
      geom_col(width=.5,fill="tomato3") +
      ggtitle("Top Frequent Words")+
      xlab(NULL) +
      ylab("Word Frequency")+
      scale_fill_brewer()+
      coord_flip()
```


The most frequent word "friend" has a frequency way much higher the 2nd most frequent word "friend". That means friends plays an indispensible role in almost every people's life. Human beings are social animals, most of them can not live without friends. 


Then, I want know as people are getting old, how will their source of happiness change. I will look at top frequent words for people in different ages. 


```{r, warning=FALSE, message=FALSE,echo=FALSE}
hm_bigrams <- hm_data %>%
  filter(count != 1) %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

bigram_counts <- hm_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  count(word1, word2, sort = TRUE)
```


```{r,echo=FALSE}
# bigram_graph <- bigram_counts %>%
#       slice(1:100) %>%
#       graph_from_data_frame()
#     
#     set.seed(123)
#     
#     x <- grid::arrow(type = "closed", length = unit(.1, "inches"))
#     
#     ggraph(bigram_graph, layout = "fr") +
#       geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
#                      arrow = x, end_cap = circle(.05, 'inches')) +
#       geom_node_point(color = "skyblue", size = 3) +
#       geom_node_text(aes(label = name), repel = TRUE) +
#       theme_void()
```

```{r,echo=FALSE,fig.height=10}
hm_data_age_20 <- hm_data[which(hm_data$age > 10 & hm_data$age < 21),]
bag_of_words_age_20 <-  hm_data_age_20 %>%
  unnest_tokens(word, text)
word_count_age_20 <- bag_of_words_age_20 %>%
  count(word, sort = TRUE)

hm_data_age_30 <- hm_data[which(hm_data$age < 31 & hm_data$age > 20),]
bag_of_words_age_30 <-  hm_data_age_30 %>%
  unnest_tokens(word, text)
word_count_age_30 <- bag_of_words_age_30 %>%
  count(word, sort = TRUE)

hm_data_age_40 <- hm_data[which(hm_data$age > 30 & hm_data$age <41 ),]
bag_of_words_age_40 <-  hm_data_age_40 %>%
  unnest_tokens(word, text)
word_count_age_40 <- bag_of_words_age_40 %>%
  count(word, sort = TRUE)

hm_data_age_50 <- hm_data[which(hm_data$age > 40 & hm_data$age < 51 ),]
bag_of_words_age_50 <-  hm_data_age_50 %>%
  unnest_tokens(word, text)
word_count_age_50 <- bag_of_words_age_50 %>%
  count(word, sort = TRUE)

hm_data_age_60 <- hm_data[which(hm_data$age > 50 & hm_data$age < 61 ),]
bag_of_words_age_60 <-  hm_data_age_60 %>%
  unnest_tokens(word, text)
word_count_age_60 <- bag_of_words_age_60 %>%
  count(word, sort = TRUE)

hm_data_age_70 <- hm_data[which(hm_data$age > 60 ),]
bag_of_words_age_70 <-  hm_data_age_70 %>%
  unnest_tokens(word, text)
word_count_age_70 <- bag_of_words_age_70 %>%
  count(word, sort = TRUE)

word_count_age_20$word <- factor(word_count_age_20$word, levels = word_count_age_20$word[order(word_count_age_20$n)])
word_count_age_30$word <- factor(word_count_age_30$word, levels = word_count_age_30$word[order(word_count_age_30$n)])
word_count_age_40$word <- factor(word_count_age_40$word, levels = word_count_age_40$word[order(word_count_age_40$n)])
word_count_age_50$word <- factor(word_count_age_50$word, levels = word_count_age_50$word[order(word_count_age_50$n)])
word_count_age_60$word <- factor(word_count_age_60$word, levels = word_count_age_60$word[order(word_count_age_60$n)])
word_count_age_70$word <- factor(word_count_age_70$word, levels = word_count_age_70$word[order(word_count_age_70$n)])

p1 <-word_count_age_20 %>%
      slice(1:15) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      geom_col() +
      ggtitle("Age From 10-20")+
      xlab(NULL) +
      ylab("Word Frequency")+
      coord_flip()

p2 <- word_count_age_30 %>%
      slice(1:20) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      geom_col() +
      ggtitle("Age From 21-30")+
      xlab(NULL) +
      ylab("Word Frequency")+
      coord_flip()
p3 <- word_count_age_40 %>%
      slice(1:20) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      geom_col() +
      ggtitle("Age From 31-40")+
      xlab(NULL) +
      ylab("Word Frequency")+
      coord_flip()
p4 <- word_count_age_50 %>%
      slice(1:20) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      geom_col() +
      ggtitle("Age From 41-50")+
      xlab(NULL) +
      ylab("Word Frequency")+
      coord_flip()
p5 <- word_count_age_60 %>%
      slice(1:20) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      geom_col() +
      ggtitle("Age From 51-60")+
      xlab(NULL) +
      ylab("Word Frequency")+
      coord_flip()
p6 <- word_count_age_70 %>%
      slice(1:20) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      geom_col() +
      ggtitle("Age Over 60")+
      xlab(NULL) +
      ylab("Word Frequency")+
      coord_flip()


grid.arrange(p1, p2,p3,p4,p5,p6, nrow = 3, top = "Top 20 Words for People in Different Age Groups")
```
\newline
Other than the top frequent words all people are talking about, teenagers also talk about "game","event", "girlfriend", "finished", "college", "exam" frenquently. \newline


As for people in 20s, they talk more about "family", "home", "job", "night". \newline
For people in 30s, "friend", "family" are still top frequent words. Other than that, "son", "daughter", "wife", "husband" become top frequent words. \newline


For people in 40s, their top frequent words are similar to those of people in 30s. \newline
For people who are older than 50, their top frequent words are still relating to family and friends, which are "friend", "daughter", "husband", "son", "home", "wife".And there are some new words appeared in the list, which are "visit", "dog", "love". \newline


As we can see from these top frequent words list, some words are relating to each other. For example, "exam" will be associated with "school" in our common sense. Next, I want to know which words are correlated. 



```{r,echo=FALSE}
hm_data$sentence_length <- sapply(strsplit(hm_data$original_hm, " "), length)
```


```{r,echo=FALSE,message=FALSE,warning=FALSE}
ggplot(hm_data, aes(x=age,color=gender, y=sentence_length)) +
  geom_point(binaxis = "y", stackdir = "center",size=.15) +
  ggtitle("Sentence Length Overview")+
  scale_x_discrete(breaks=c("10","20","30","40","50","60","70"),
        labels=c("10", "20", "30","40","50","60","70"))
  
  theme(axis.text.x = element_text(color="#993333",size=8, angle=45))
```


This graph shows different wording behavior for people in different age groups. It implies that people who are younger than 40 years old tend to write more words in this survey. And there are some extremely long texts writen by people in 20-30 age group.


### Create bigrams using the text data

```{r,echo = FALSE}
hm_bigrams <- hm_data %>%
  filter(count != 1) %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

bigram_counts <- hm_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  count(word1, word2, sort = TRUE)
```


```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(widyr)
a <- hm_bigrams
a<- a$bigram
a <- unlist(strsplit(a," "))
#dat <- data_frame(group = rep(1:37829), factor = hm_data$count,
dat <- data_frame(group = rep(1:(979610/2), each = 2),
                  letter = a)
title_word_pairs<-pairwise_count(dat, letter, group)

desc_word_pairs <-pairwise_count(dat, letter,group, sort = TRUE, upper = FALSE)

```



```{r,echo=FALSE,message=FALSE, warning=FALSE}
library(ggplot2)
library(igraph)
library(ggraph)
set.seed(1234)
desc_word_pairs %>%
  filter(n >= 150) %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = n, edge_width = n), edge_colour = "darkred") +
  geom_node_point(size = 5) +
  ggtitle("Correlation for Bigrams")+
  geom_node_text(aes(label = name), repel = TRUE,
                 point.padding = unit(0.2, "lines")) +
  theme_void()
```



As we can see from this correlation map, "friend" is correlated with many words. That means people did many things with their friends. Also, "video"" is correlated with "game" and "played", they means people always use these three words together. And "offer", "job", "interview" are correlated with each other. 

```{r,echo=FALSE}
# keyword_cors <- nasa_keyword %>%
#   group_by(keyword) %>%
#   filter(n() >= 50) %>%
#   pairwise_cor(keyword, id, sort = TRUE, upper = FALSE)
# 
# #keyword_cors
```







```{r,echo=FALSE}
ggplot(hm_bigrams, aes(x=ground_truth_category)) +
  geom_density() 
```


```{r,echo=FALSE}
  # temp <- bag_of_words  %>%
  #    count(!!as.name(bag_of_words$gender), word) %>%
  #     group_by(!!as.name(bag_of_words$gender)) %>%
  #    mutate(proportion = n / sum(n)) %>%
  #     select(-n) %>%
  #     spread(!!as.name(bag_of_words$gender), proportion)

  #    ggplot(temp,
  #           aes_string(x = colnames(temp)[2], y = colnames(temp)[3]),
  #           color = abs(colnames(temp)[3] - colnames(temp)[2])) +
  #    geom_abline(color = "gray40", lty = 2) +
  #    geom_jitter(alpha = 0.1, size = 1, width = 0.3, height = 0.3) +
  #   geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5)
  #   scale_x_log10(labels = percent_format()) +
  #   scale_y_log10(labels = percent_format()) +
  #  scale_color_gradient(limits = c(0, 0.001), low = "darkslategray4", high = "gray75") +
  #  theme(legend.position="none")
```


```{r,echo=FALSE}
# 
# hm_bigrams %>%
#       count(!!as.name(gender), bigram, sort = TRUE) %>%
#       group_by(!!as.name(gender)) %>%
#       top_n(10) %>%
#       ungroup() %>%
#       mutate(bigram = reorder(bigram, n)) %>% 
#       ggplot(aes(bigram, n, fill = !!as.name(gender))) +
#       geom_col(show.legend = FALSE) +
#       facet_wrap(as.formula(paste("~", gender)), ncol = 2, scales = "free") +
#       coord_flip()
```

